Fitting the Undetected: Light-curve Feature Estimation in the Presence of Non-detections

### 2013-03-26 tex/ms.tex
notes to selves

% Define the document class. aastex for manuscript preparation, emulateapj for making it look polished.
% \documentclass[12pt,preprint2]{aastex}
%\documentclass[12pt,a4paper, iop,onecolumn,numberedappendix]{emulateapj}
\documentclass[12pt,preprint]{aastex}

@@

% And similarly, one (less jarring, with fewer symbols and no boldface) command
% for each one of us to leave comments in the main text.
\newcommand{\james}[1] { \textcolor{blue} {
\ensuremath{\blacklozenge} {\bf james:}  {#1}
\ensuremath{\blacklozenge} } }

\newcommand{\hogg}[1] { \textcolor{darkorange} {
\ensuremath{\blacksquare} {\bf hogg:}  {#1}
\ensuremath{\blacksquare} } }

\newcommand{\dan}[1] { \textcolor{darkgreen} {
\ensuremath{\bigstar} {\bf dan:}  {#1}
\ensuremath{\bigstar} } }

\newcommand{\joey}[1] { \textcolor{red} {
\ensuremath{\clubsuit} {\bf joey:}  {#1}
\ensuremath{\clubsuit} } }%\documentclass[manuscript]{aastex}

@@

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,%
      trim=3cm 12cm 5cm 3cm, clip=true]{gm/gm.pdf}
  \end{center}
  \caption{The graphical representation of the probability distribution.
    \label{fig:graph}}
\end{figure}

\clearpage
\begin{figure}
\begin{center}
\includegraphics[angle=0,width=6.5in]{../plots/mira_simulated.pdf}
\end{center}
\caption{ Folded light curves for data simulated from the Mira variable ASAS 235627-4947.2 using the prescription in \S\ref{ss:mirasim}.  Blue tick marks along the bottom axis denote phases where there were non-detections.  As the original flux measurements are dimmed by higher factors, the troughs of the sinusoidal light curve are censored, resulting in an incomplete view of the data.  \label{fig:mirasim}}
\end{figure}

>>>>

\documentclass[12pt,preprint]{aastex}

@@

% And similarly, one (less jarring, with fewer symbols and no boldface) command
% for each one of us to leave comments in the main text.
\newcommand{\james}[1] { \textcolor{blue} {
\ensuremath{\blacklozenge} {\bf james says:}  {#1}
\ensuremath{\blacklozenge} } }

\newcommand{\hogg}[1] { \textcolor{darkorange} {
\ensuremath{\blacksquare} {\bf hogg says:}  {#1}
\ensuremath{\blacksquare} } }

\newcommand{\dan}[1] { \textcolor{darkgreen} {
\ensuremath{\bigstar} {\bf dan says:}  {#1}
\ensuremath{\bigstar} } }

\newcommand{\joey}[1] { \textcolor{red} {
\ensuremath{\clubsuit} {\bf joey says:}  {#1}
\ensuremath{\clubsuit} } }%\documentclass[manuscript]{aastex}

@@

\clearpage
\begin{figure}
  \begin{center}
    [\hogg{PUT FIGURE HERE}]
  \end{center}
  \caption{An example of why this project is necessary.  The points are... \hogg{this should be a figure showing heavily censored data and a traditional fit to them, folded AND UNFOLDED, showing that the traditional fit is way wrong.}\label{fig:badfit}}
\end{figure}

\clearpage
\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth,%
      trim=3cm 12cm 5cm 3cm, clip=true]{gm/gm.pdf}
  \end{center}
  \caption{The graphical representation of the probability distribution.\label{fig:graph}}
\end{figure}

\clearpage
\begin{figure}
\begin{center}
\includegraphics[angle=0,width=6.5in]{../plots/mira_simulated.pdf}
\end{center}
\caption{ Folded light curves for data simulated from the Mira variable ASAS 235627-4947.2 using the prescription in \S\ref{ss:mirasim}.  Blue tick marks along the bottom axis denote phases where there were non-detections.  As the original flux measurements are dimmed by higher factors, the troughs of the sinusoidal light curve are censored, resulting in an incomplete view of the data.  \hogg{This figure needs to show the OLD and NEW best-fit lightcurve models too!}\label{fig:mirasim}}
\end{figure}

\clearpage
\begin{figure}
  \begin{center}
    [\hogg{PUT FIGURE HERE}]
  \end{center}
  \caption{A real-data example.  This is the same source as that shown in \figurename~\ref{fig:badfit} but now showing the results of...\label{fig:goodfit}}
\end{figure}

\clearpage
\begin{figure}
  \begin{center}
    [\hogg{PUT FIGURE HERE}]
  \end{center}
  \caption{Another few real-data examples; in each case the method presented here either matches the traditional method or is substantially better.\label{fig:examples}}
\end{figure}
